working title Compatibility system and stigma size are the main predictors of heterospecific pollen effect

### 2019-03-06 Manuscript_draft/Manuscript_draft.Rmd
edits

Foreign pollen effect was studied through two different treatments, one with 50% conspecific pollen and 50% heterospecific pollen and a second one with 100% foreign pollen in order to see if foreign pollen can trigger fruit production by itself or even seeds through ovule usurpation. Therefore, we perfomed 180 different heterospecific treatments (N=10). Seed set was the proxy of effect for all our treatments. Moreover, hand cross-pollination (between individuals of the same species), hand self-pollination, apomixis (bagged emasculated flowers) and natural selfing were tested for each species (N=10). For the treatments with foreign pollen and hand cross-pollination, flowers were emasculated the day prior anthesis and hand pollinated next day with a toothpick. Hand-pollination was conducted with 3-4 gentle touches on the stigma surface. For each species 20 anthers were collected and their pollen counted with a hemocytometer, each anther was counted 4 times and then an average of these counts was performed. Once, the average number of pollen grains per anther was known, the proportion of anthers per mix was calculated in order to achieve a 50-50% mix.  In order to confirm that the treatments applied were the desire proportions, the total stigmatic load of pollen was counted and the proportions calculated between the two species of the mix. Therefore, 20 different heterospecific crosses 50-50% were counted for all the focal species with crosses of just one species of the other two families (N=3).

>>>>

Foreign pollen effect was studied through two different treatments, one with 50% conspecific pollen and 50% heterospecific pollen and a second one with 100% foreign pollen in order to see if foreign pollen can trigger fruit production by itself or even seeds through ovule usurpation. Therefore, we perfomed 180 different heterospecific treatments (N=10). Seed set was the proxy of effect for all our treatments. Moreover, hand cross-pollination (between individuals of the same species), hand self-pollination, apomixis (bagged emasculated flowers) and natural selfing were tested for each species (N=10). For the treatments with foreign pollen and hand cross-pollination, flowers were emasculated the day prior anthesis and hand pollinated next day with a toothpick. Hand-pollination was conducted with 3-4 gentle touches on the stigma surface. For each species 20 anthers were collected and their pollen counted with a hemocytometer, each anther was counted 4 times and then an average of these counts was performed. Once, the average number of pollen grains per anther was known, the proportion of anthers per mix was calculated in order to achieve a 50-50% mix.  To confirm that the treatments applied were the desire proportions, the total stigmatic load of pollen was counted and the proportions calculated between the two species of the mix. Because pollen from the same family was difficult to distinguish, and we expected similar properties in mixing, we counted pollen from just one randomly selected species within each donor family different to the focal's family (N=3).

### 2019-03-06 Manuscript_draft/Manuscript_draft.tex
edits

Foreign pollen effect was studied through two different treatments, one
with 50\% conspecific pollen and 50\% heterospecific pollen and a second
one with 100\% foreign pollen in order to see if foreign pollen can
trigger fruit production by itself or even seeds through ovule
usurpation. Therefore, we perfomed 180 different heterospecific
treatments (N=10). Seed set was the proxy of effect for all our
treatments. Moreover, hand cross-pollination (between individuals of the
same species), hand self-pollination, apomixis (bagged emasculated
flowers) and natural selfing were tested for each species (N=10). For
the treatments with foreign pollen and hand cross-pollination, flowers
were emasculated the day prior anthesis and hand pollinated next day
with a toothpick. Hand-pollination was conducted with 3-4 gentle touches
on the stigma surface. For each species 20 anthers were collected and
their pollen counted with a hemocytometer, each anther was counted 4
times and then an average of these counts was performed. Once, the
average number of pollen grains per anther was known, the proportion of
anthers per mix was calculated in order to achieve a 50-50\% mix. In
order to confirm that the treatments applied were the desire
proportions, the total stigmatic load of pollen was counted and the
proportions calculated between the two species of the mix. Therefore, 20
different heterospecific crosses 50-50\% were counted for all the focal
species with crosses of just one species of the other two families
(N=3).

>>>>

Foreign pollen effect was studied through two different treatments, one
with 50\% conspecific pollen and 50\% heterospecific pollen and a second
one with 100\% foreign pollen in order to see if foreign pollen can
trigger fruit production by itself or even seeds through ovule
usurpation. Therefore, we perfomed 180 different heterospecific
treatments (N=10). Seed set was the proxy of effect for all our
treatments. Moreover, hand cross-pollination (between individuals of the
same species), hand self-pollination, apomixis (bagged emasculated
flowers) and natural selfing were tested for each species (N=10). For
the treatments with foreign pollen and hand cross-pollination, flowers
were emasculated the day prior anthesis and hand pollinated next day
with a toothpick. Hand-pollination was conducted with 3-4 gentle touches
on the stigma surface. For each species 20 anthers were collected and
their pollen counted with a hemocytometer, each anther was counted 4
times and then an average of these counts was performed. Once, the
average number of pollen grains per anther was known, the proportion of
anthers per mix was calculated in order to achieve a 50-50\% mix. To
confirm that the treatments applied were the desire proportions, the
total stigmatic load of pollen was counted and the proportions
calculated between the two species of the mix. Because pollen from the
same family was difficult to distinguish, and we expected similar
properties in mixing, we counted pollen from just one randomly selected
species within each donor family different to the focal's family (N=3).
